\documentclass[12pt]{article}

\title{SDM-22 Data Acquisition Package\\User Manual}
\author{Sun Devil Motorsports DAQ Team\\Benji Miller, Joshua Tenorio}
\date{Revised \today}

\begin{document}
\maketitle
\tableofcontents
\section{System Overview}
Sun Devil Motorsports' Data Acquisition team is responsible for collecting and analyzing data from the car.

This year we have developed a very poggers DAQ package.
\pagebreak
\section{Usage}
To begin logging data, plug in the battery cable of the main board into the ECU's 5V output.
If powered on, the onboard LED on the main board's Teensy will be lit up.
Data will be logged to the Teensy's micro SD card on the main board.
The most recent run will have the largest run number on the micro SD card.

\textbf{Do not have USB power and 5V from the ECU plugged in at the same time!}
Doing so may risk power flowing back into the USB port.
This is because VUSB and VCC on the Teensy boards are connected to each other.

\textbf{Please note that it takes a large amount of force to plug in our connectors}.
You'll hear a click once it is properly plugged in.
\section{Wiring and Pinouts}
\subsection{Main Board}
\subsection{Wheel Boards}
\subsection{Wire Pinouts}
Serial (VBAT)

\begin{tabular}{|c|c|c|c|}
\hline
Red & Black & Blue & Yellow \\
\hline
1 & 2 & 3 & 4 \\
\hline
VIN & GND & TX & RX \\
\hline
\end{tabular}
\vspace{1em}

\noindent Serial (3.3V)

\begin{tabular}{|c|c|c|c|}
\hline
Red & Black & Blue & Yellow \\
    \hline
1 & 2 & 3 & 4 \\
    \hline
3.3V & GND & TX & RX \\
    \hline
\end{tabular}
\vspace{1em}

\noindent i2C

\begin{tabular}{|c|c|c|c|}
\hline
Red & Black & Blue & Yellow \\
\hline
1 & 2 & 3 & 4 \\
\hline
3.3V & GND & SCL & SDA\\
\hline
\end{tabular}
\vspace{1em}

\noindent Analog

\begin{tabular}{|c|c|c|c|}
    \hline
    Red & Black & Blue \\
    \hline
    1 & 2 & 3 \\
    \hline
    3.3V & GND & Analog \\
    \hline
\end{tabular}
\vspace{1em}

\noindent Power

\begin{tabular}{|c|c|}
\hline
Red & Black \\
\hline
1 & 2 \\
\hline
VCC & GND \\
\hline
\end{tabular}
\vspace{1em}

\noindent CAN

\begin{tabular}{|c|c|}
    \hline
    Red & Black \\
    \hline
    1 & 2 \\
    \hline
    CANL & CANH \\
    \hline
\end{tabular}
\section{Software}
\section{Packing List}
In the DAQ Toolbox:
\begin{itemize}
    \item Scissors
    \item Duct Tape
    \item Electrical Tape
    \item Voltimeter
    \item Micro USB Cable
\end{itemize}
\section{Meme}
\end{document}
